Verifying Demonstrations

### 2019-03-01 paper/intro.tex
adds outline

%The paper is organized as follows.
%\Cref{system-model}, we describe our system model and summarize the desired 
%properties for crowd counting.
%We then discuss related work in terms of these properties in 
%\cref{related-work}:
%we first discuss the crowd counting methods that are classically used followed 
%by work on location proof systems.
%
%\Cref{definitions}, we formalize the notion of protest and the desired 
%verifiability and privacy properties, and in \cref{building-blocks}, we give 
%the relevant background on the building blocks of our solution.
%
%\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
%different from that originally proposed by \textcite{DistanceBounding}.
%We provide a proof of its security and formally verify it using 
%Tamarin~\cite{TamarinDB}.
%
%\Cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting 
%estimation protocol.
%We analyze its security in \cref{SecurityAnalysis} and estimate its performance 
%in \cref{PerformanceAnalysis}.
%
%Finally, we discuss our assumptions and results in \cref{Discussion} and give 
%our conclusions in \cref{Conclusion}.

>>>>

The paper is organized as follows.
In \Cref{system-model}, we describe our system model and summarize the desired 
properties for crowd counting, followed by a discussion of related work in \cref{related-work}. In \Cref{definitions}, we formalize the notion of protest and the desired verifiability and privacy properties, and in \cref{building-blocks}, we give 
the relevant background on the building blocks of our solution.
%
%\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
%different from that originally proposed by \textcite{DistanceBounding}.
%We provide a proof of its security and formally verify it using 
%Tamarin~\cite{TamarinDB}.
%
We present \CROCUS, a privacy-preserving crowd counting 
%estimation 
protocol in in \Cref{Protocol}, analyze its security in \cref{SecurityAnalysis}, and estimate its performance in \cref{PerformanceAnalysis}.
Finally, we discuss limitations and assumptions in \cref{Discussion} and give 
our conclusions in \cref{Conclusion}.
